%
% file: dedication.tex
% author: Henry Semenenko
%

\chapter*{Acknowledgements}
I would firstly like to thank Dr Chris Erven for his supervision and encouragement throughout my PhD and I am ever grateful to Dr Philip Sibson for his patience and Wikipedia-like knowledge. Thank you to Dr David Lowndes and Dr Alasdair Price for their (often not misguided) advice and Prof. John Rarity FRS for his endless inspiring tales. Thank you to Dr Djeylan Aktas, Dr Jorge Barreto, Friederike J\"{o}hlinger, Dr Alasdair Price and Lawrence Rosenfeld for taking the time to proofread this thesis.

I am indebted to each and every member of QETLabs of which there are, unfortunately, far to many to name here. 
I am incredibly appreciative of the support from the ops team, past and present, without whom I would have never been able to achieved half of the things I was able to. In particular to Lorraine, Holly, Emma, Helen, Andrea, Lin and Rebecca.

Thank you to the whole of cohort 2, Alex, Dan, Geraint, Jason, Joe, Lawrence, Lucio, Martin and Sam, who have made this journey so memorable; to Dr. Milica Prokic and Neil Simmons for providing the artwork that has been used to decorate this thesis; to Dr Graham Marshall for your help despite my continual harassment; and to Andy Murray for his unrivalled technical knowledge. 

Finally, I want to thank my family for their support, inspiration and for getting me here in one piece. Thank you to my friends for trying their best to make it more than one piece.

\clearpage