%
% File: publications.tex
% Author: Henry Semenenko
% Description: Lists the publications from the PhD
{\setlength{\parindent}{0pt} %remove the indentation
\abnormalparskip{18pt} %increase the paragraph skip length
\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}
\section*{Journals}

H. Semenenko, P. Sibson, M. G. Thompsonand C. Erven, "Interference between independent photonic integrated devices for quantum key distribution," \textit{Opt. Lett. 44, 275-278}, Jan. 2019 

H. Semenenko, P. Sibson, A. Hart, M. G. Thompson, J. G. Rarity  and C. Erven, "Chip-based measurement-device-independent quantum key distribution," \textit{arXiv:1908.08745}, Aug. 2019 

\section*{Conferences}

H. Semenenko, P. Sibson, A. Hart, M. G. Thompson and C. Erven, ``Chip-based measurement-device-independent quantum key distribution,'' \textit{oral presentation}, QCrypt, Aug. 2019

H. Semenenko, P. Sibson, M. G. Thompson and C. Erven, ``Integrated devices for measurement-device-independent quantum key distribution,'' \textit{oral presentation}, CLEO, Apr. 2019

P. Sibson, D. Lowndes, S. Frick, A. Price, H. Semenenko, F. Raffaelli, D. Llewellyn, J. Kennard, Y. Ou, F. Ntavou, E. Hugues Salas, A. Hart, R. Collins, A. Laing, C. Erven, R. Nejabati, D. Simeonidou, M. G. Thompson and J. G. Rarity, ``Networked Quantum-Secured Communications with Hand-held and Integrated Devices: Bristol’s Activities in the UK Quantum Communications Hub,'' \textit{oral presentation given by P. Sibson}, QCrypt, Sep. 2017

H. Semenenko, P. Sibson, J. Barreto and C. Erven, ``Towards Accessible Metropolitan Quantum Secure Communication,'' \textit{oral presentation}, Young Quantum Information Scientist, Sep. 2017 

A. Vaquero-Stainer, R. A. Kirkwood, V. Burenkov, C. J. Chunnilall, A. G Sinclair, A. Hart, H. Semenenko, P. Sibson, C. Erven and M. G. Thompson, ``Measurements towards providing security assurance for a chip-scale QKD system,'' \textit{oral presentation given by A. Vaquero-Stainer}, Proc. SPIE 10674, Quantum Technologies, May 2018

H. Semenenko, P. Sibson, M. G. Thompson and C. Erven, ``Integrated Photonic Devices for Measurement-Device-Independent Quantum Key Distribution,'' \textit{poster}, QCrypt, Aug. 2018

A. Hart, H. Semenenko, S. Frick, C. Erven, D. Lowndes, P. Sibson, M. Thompson and J. G. Rarity, ``Small Form Factor, Low Cost Electronics for Chip Scale and Handheld Quantum Key Distribution Systems,'' \textit{poster}, QCrypt, Aug. 2018

D. V. Aktas, P. Sibson, D. Lowndes, S. Frick, A. Price, H. Semenenko, F. Raffaelli, D. Llewellyn, J. Kennard, Y. Ou, F. Ntavou, E. Hugues Salas, A. Hart, R. Collins, A. Laing, C. Erven, R. Nejabati, D. Simeonidou, M. G. Thompson and J. G. Rarity, ``A Metropolitan Quantum Network with Hand-Held and Integrated Devices,'' \textit{poster presentation given by D. V. Aktas}, GDR IQFA, Nov. 2018
}
\clearpage